\documentclass[12pt]{article}
\usepackage{lipsum}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage[margin=1in]{geometry} % Set 1-inch margins
\usepackage{graphicx} % Required for inserting images
\pagestyle{empty}

\newcommand{\contact}[3]{{#1} \hspace{0.05em} \href{#2}{#3} \newline}

%%%%%%%%% Company-specific info %%%%%%%%%
\newcommand{\companyname}{}
\newcommand{\position}{}

\begin{document}

\noindent\begin{minipage}[t]{0.3\textwidth}
  \vspace{0pt}
  \begin{flushleft}
      {\LARGE \textbf{Lucas Khan}} \newline
      {\large Mathematics Student, University of Waterloo} \newline \newline
      \contact{\faEnvelopeSquare}{mailto:lfkhan@uwaterloo.ca}{lfkhan@uwaterloo.ca}
      \contact{\faLinkedinSquare}{https://linkedin.com/in/lucas-khan-101a51253}{lucas-khan-101a51253}
      \contact{\faGithubSquare}{https://github.com/1-mbps}{1-mbps}
  \end{flushleft}
\end{minipage}%
\hspace{0.07\textwidth}% Adjust the gap between columns
\begin{minipage}[t]{0.63\textwidth}
  \vspace{0pt}
  \rule{\linewidth}{3px} % 3px black line at the top
  \newline \newline
  Dear hiring manager:
  \newline \newline
  Greetings! My name is Lucas Khan, and I am a second-year mathematics student at the University of Waterloo. I’m writing to express my interest in your opening for a \position this coming summer.
  \newline \newline
  I've been working on machine learning projects for around four years. I was first exposed to the field in high school, where, for a science project, I developed machine learning algorithms for detecting (based on their vital signs) potentially critical patients in hospital emergency rooms. With this project, I was able to represent my school in science fairs in Singapore, Taiwan, and Malaysia, and was fortunate enough to win a few awards.
  \newline \newline
  Since entering university, I've worked as a natural language processing engineer at the Region of Waterloo. During my time there, I worked with large language models, leading development on an education chatbot that will soon be rolled out to several schools around the regional municipality of Waterloo. I also worked on a natural language chatbot that will soon be added to many regional government websites. On these projects, my work involved not only developing novel machine learning methods, but also building the infrastructure around ML tools and integrating them with various systems. I think that this kind of background would be useful in a machine learning engineer role such as this one.
  \newline \newline
  Thank you for taking the time to read this letter. [last_line]
  \newline \newline
  Sincerely,
  \newline \newline \newline
  Lucas Khan
  % \newline \newline \small \textit{Note: in case this is relevant, I am legally authorized to work in the US and will not require any visa sponsorship.}
\end{minipage}

\end{document}
