\documentclass[12pt]{article}
\usepackage{lipsum}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage[margin=1in]{geometry} % Set 1-inch margins
\usepackage{graphicx} % Required for inserting images
\pagestyle{empty}

\newcommand{\contact}[3]{{#1} \hspace{0.05em} \href{#2}{#3} \newline}

%%%%%%%%% Company-specific info %%%%%%%%%
\newcommand{\companyname}{}
\newcommand{\position}{}

\begin{document}

\noindent\begin{minipage}[t]{0.3\textwidth}
  \vspace{0pt}
  \begin{flushleft}
      {\LARGE \textbf{Lucas Khan}} \newline
      {\large Mathematics Student, University of Waterloo} \newline \newline
      \contact{\faEnvelopeSquare}{mailto:lfkhan@uwaterloo.ca}{lfkhan@uwaterloo.ca}
      \contact{\faLinkedinSquare}{https://linkedin.com/in/lucas-khan-101a51253}{lucas-khan-101a51253}
      \contact{\faGithubSquare}{https://github.com/1-mbps}{1-mbps}
  \end{flushleft}
\end{minipage}%
\hspace{0.07\textwidth}% Adjust the gap between columns
\begin{minipage}[t]{0.63\textwidth}
  \vspace{0pt}
  \rule{\linewidth}{3px} % 3px black line at the top
  \newline \newline
  Dear hiring manager:
  \newline \newline
  Greetings! My name is Lucas Khan, and I am a second-year mathematics student at the University of Waterloo. I’m writing to express my interest in your opening for a \position this coming summer.
  \newline \newline
  I’ve worked on various software projects for around five years. I taught myself data structures and algorithms in high school, and in my final two years, competed at the national level in programming contests in the Philippines (my home country). Following these competitions, I participated in training camps for the International Olympiad in Informatics, where I studied advanced topics such as constructive algorithms and graph theory.
  \newline \newline
  Since entering university, I’ve worked as a natural language processing engineer at the Region of Waterloo. During my time there, I led development on an AI education tool for local schools, and contributed to a chatbot that will soon be added to many regional government websites. My work on these projects involved building the infrastructure around AI tools, which can be very unwieldy and unpredictable. This, I think, has honed my skills in writing efficient code for complex systems, which I hope would be useful in this role at \companyname.
  \newline \newline
  Thank you for taking the time to read this letter. [last_line]
  \newline \newline
  Sincerely,
  \newline \newline \newline
  Lucas Khan
  % \newline \newline \small \textit{Note: in case this is relevant, I am legally authorized to work in the US and will not require any visa sponsorship.}
\end{minipage}

\end{document}
